Analysis of the \\ Information Security Job Landscape \\ in Austria

### 2020-05-29 paper/paper.tex
Explain false positives.
Fix spelling.

The second most common requirement is an apprenticeship (“\german{Ausbildung}”) at around 36\%, followed by the Matura with 22\%. After a manual review of the 4\% belonging to apprenticeship (“\german{Lehre}”), these seem to be mostly false positives, at least in our case when only taking information security jobs into account.

>>>>

The second most common requirement is an apprenticeship (“\german{Ausbildung}”) at around 36\%, followed by the “\german{Matura}” with 22\%. After a manual review of the 4\% belonging to apprenticeship (“\german{Lehre}”), these seem to be mostly false positives, at least in our case when only taking information security jobs into account. The false positives in this case are due to the fact the the term “\german{Lehre}” is not only used to describe an apprenticeship but also teaching -- also referred to as “\german{Lehre}” -- positions.
